Towards a Tool for Verified Hardware Construction

### 2014-06-10 paper.tex
add more english that appeared to be missing

In \cite{blackboxed} \cite{languagebased} they discuss mechanisms for architectural and language support for mitigating the
leakage of information through side channels. They take the approach of inserting time stops in order to prevent implicit
leaks from control flow structures.

In \cite{languagebased} they described ways to add a type system to a small imperative language in order to mitigate the leakage of timing information.
Ideally these hardware concerns shouldn't leak beyond the hardware level, and they grapple with this in their analysis of the technique.

@@

There is a prototype implementation of ideas discussed in the final section available. It is currently
written in Idris one of the more practical dependently typed programming language.

@@

Most previous approaches have not been practical enough to use for building real designs. Fe-Si is as close to
complete but is still unfortunately just a toy. The DSL approach has important limitations and requires
programming in an awkward monadic style inside of the theorem proof system Coq. Ideally we would like to take the 
simple core described in the Fe-Si work, but extend it in a few key ways. First we would like to add a surface language
that will give us the ability to add more complicated features than the limited Fe-Si. We will also like to make modules first class
entities that express information about the functionality of the circuit as well as

We have experimented with a few different designs, and am still considering which is the best way forward.
So far we have not made a decision on which is best, but have noticed some important trade offs in the process
of implementing

>>>>

In \cite{blackboxed} \cite{languagebased} they discuss mechanisms for architectural and language support for mitigating the
leakage of information through side channels. They take the approach of inserting time stops in order to prevent implicit
leaks from control flow structures. In \cite{languagebased} they described ways to add a type system to a small imperative language in 
order to mitigate the leakage of timing information. Ideally these concerns shouldn't leak beyond the hardware level, and they grapple with this in their analysis of the technique.

@@

There is a prototype implementation of ideas discussed in the final section available. It is currently
written in Idris (which is one of the more practical dependently typed programming languages).

@@

Most previous approaches have not been practical enough to use for building real designs. Fe-Si is as close to
complete but is still unfortunately just a toy. The DSL approach has important limitations and requires
programming in an awkward monadic style inside of the theorem proof system Coq. Ideally we would like to take the 
simple core described in the Fe-Si work, but extend it in a few key ways. First we would like to add a surface language
that will give us the ability to add more complicated features than the limited Fe-Si. We will also like to make modules first class
entities that express information about the functionality of the circuit as well so that we can use such information when proving
properties about designs.

We have experimented with a few different designs, and am still considering which is the best way forward.
So far we have not made a decision on which is best, but have noticed some important trade offs in the process
of implementing prototypes. Many of the naive designs don't work because they lose precious typing information
that is essential for proving properties about the design. It has become apparent that many of the decisions made
by Adam Chilpalia's work are important. We will use the same approach of using a denontational approach, and relying
on properties of the metalanguage such as strong normalization, and its type system to assure that our designs are
correct by construction. We could of course elaborate our language to a core calculus and implement our own checker
but it is important to not duplicate effort early in the research process, and should piggy back on existing work.
For now we are translating directly to Idris source language, but it exposes its core calculus and checker as a
library we can eventually use if we want to piggyback on their implementation effort. We also want to model his
approach to slowly adding and proving the correctness of optimizations beyond the simple ones performed in \cite{fesi}.

One of the long term goals is a verified framework for abstract interpretation a powerful analysis technique, but for
now we will continue on in the style of Chilpalia.One of the big departures from FeSi is that we want to provide a back door 
into the full theorem proving environment which will allow for designers or verifiers to add more complex theorems, and maintain 
the power provided by a full proof assitant such as Coq.
